%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}



\cvname{Sathish Kumar \\ \\ Narayanan} % Your name
\cvjobtitle{Full Stack Developer} % Job title/career

\cvlinkedin{https://linkedin.com/in/ragavsathish}
\cvnumberphone{+358 40 169 2503} % Phone number
\cvsite{http://github.com/ragavsathish}
\cvmail{ragav.sathish@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2014 - 2018 \\}
        {MSc., Life Science Technologies}
        {\href{http://www.aalto.fi/}{Aalto University}}
        {Espoo, Finland}
        {GPA: 3.93/5 \\ \textit{Specialization: Bioinformatics}}
	\twentyitem
    	{2006 - 2010}
        {BEng., Computer Science and Engineering}
        {\href{https://www.annauniv.edu/}{Anna University}}
        {Chennai, TamilNadu, India}
        {GPA: 80\% First Class with Distinction}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------


\section{Experience}

\begin{twenty} % Environment for a list with descriptions
       
	\twentyitem
    	{Dec 2017 - \\Jul2018}
        {Full Stack Developer}
        {\href{http://www.seppo.io/}{Seppo}}
        {Seppo.io - Gamified outdoor learning platform}
        {
        {\begin{itemize}
        \item Refactored existing rails view to Single Page Application(SPA) using Material-ui-next, React and Redux 
        \item Developed business reporting by customizing admin-on-rest (SPA framework built on REST service)
    \end{itemize}}
        }
        
     \twentyitem
   		{2010 - 2014}
        {Software Developer}
        {\href{http://www.infosys.com/}{Infosys}}
        {}
        {4 years of JEE developer experience \\ 
        \begin{itemize}
        \item  Refactored legacy inventory management for performance optimization. 
        \item Developed generic User Acceptance Testing using Cucumber-JVM and built a maven based CI pipeline using Apache Continuum.  
        \item Touch to pay wrist band - The American express prepaid payment solution for Disney. Developed baseline project architecture by leveraging spring web MVC framework.
Provided support for SAML assertion for authentication and authorization of user accounts. Unit testing with Easy mock and Junit.
        \end{itemize}
    	}
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}


\section{Research}
\begin{twenty}
	\twentyitem
    	{2015 - 2017}
        {Graduate Research Assistant}
        {\href{http://ala-laurila.biosci.helsinki.fi/}{Ala-Laurila Lab, Aalto University}}
        {}
        {
        {\\Developed a Matlab based \href{https://github.com/Schwartz-AlaLaurila-Labs/sa-labs-analysis}{\textbf{data analysis toolbox}} for multi-unit neuronal recordings. Assembled a four electrode patch clamp system to quantify neural circuits in retina.}
        }
    \twentyitem
   		{Jan - May '17}
        {Graduate Teaching Assistant}
        {\href{http://www.aalto.fi}{Aalto University}}
        {}
        {
        {\\\textbf{Neural Information processing - }Evaluated computational and simulation assignments on  nonlinear models. The topics include visual information processing, statistical analysis of spike trains \& stimulus coding and applying information theoretic approach to quantify spike trains
    }
        }
\end{twenty}

\section{Open Source}
\begin{twenty}
	\twentyitem
    	{Jan 2018 - \\Preesent}
        {Scientific Programmer}
        {\href{http://ala-laurila.biosci.helsinki.fi/}{Ala-Laurila Lab, Aalto University}}
        {}
        {
        {\\Actively maintaining open source Github organizations, \href{https://github.com/ala-laurila-lab}{Ala-Laurila-Lab} and \href{https://github.com/Schwartz-AlaLaurila-Labs/}{Schwartz-Ala-Laurila Labs} - An open science collaboration between Schwartz Lab, Northwestern University, USA and Ala-Laurila Lab, Aalto University, Finland.
    }
        }
\end{twenty}

\end{document} 
